---
title: "07-Bismark-Mox"
output: html_document
---

Running Bismark with  –score_min L,0,-0.6 
Run by Sam

http://onsnetwork.org/kubu4/2018/09/13/dna-methylation-analysis-olympia-oyster-whole-genome-bsseq-bismark-pipeline-comparison/


```
#!/bin/bash
## Job Name
#SBATCH --job-name=20180913_bismark
## Allocation Definition
#SBATCH --account=srlab
#SBATCH --partition=srlab
## Resources
## Nodes
#SBATCH --nodes=1
## Walltime (days-hours:minutes:seconds format)
#SBATCH --time=30-00:00:00
## Memory per node
#SBATCH --mem=120G
##turn on e-mail notification
#SBATCH --mail-type=ALL
#SBATCH --mail-user=samwhite@uw.edu
## Specify the working directory for this job
#SBATCH --workdir=/gscratch/scrubbed/samwhite/20180913_oly_WGBSseq_bismark

# Load Python Mox module for Python module availability

module load intel-python3_2017

# Document programs in PATH (primarily for program version ID)

date >> system_path.log
echo "" >> system_path.log
echo "System PATH for $SLURM_JOB_ID" >> system_path.log
echo "" >> system_path.log
printf "%0.s-" {1..10} >> system_path.log
echo ${PATH} | tr : \\n >> system_path.log


# Directories and programs

bismark_dir="/gscratch/srlab/programs/Bismark-0.19.0"
trimmed="/gscratch/scrubbed/samwhite/data/O_lurida/BSseq/whole_genome_BSseq_reads/20180830_trimgalore"
bowtie2_dir="/gscratch/srlab/programs/bowtie2-2.3.4.1-linux-x86_64/"
genome="/gscratch/scrubbed/samwhite/data/O_lurida/BSseq/20180503_oly_genome_pbjelly_sjw_01_bismark/"
samtools="/gscratch/srlab/programs/samtools-1.9/samtools"

# Run bismark using bisulftie-converted genome
# Converted genome from 20180503 - by me:
# http://onsnetwork.org/kubu4/2018/05/08/bs-seq-mapping-olympia-oyster-bisulfite-sequencing-trimgalore-fastqc-bismark/

${bismark_dir}/bismark \
--path_to_bowtie ${bowtie2_dir} \
--genome ${genome} \
--score_min L,0,-0.6 \
-p 28 \
--non_directional \
${trimmed}/1_ATCACG_L001_R1_001_trimmed.fq.gz \
${trimmed}/2_CGATGT_L001_R1_001_trimmed.fq.gz \
${trimmed}/3_TTAGGC_L001_R1_001_trimmed.fq.gz \
${trimmed}/4_TGACCA_L001_R1_001_trimmed.fq.gz \
${trimmed}/5_ACAGTG_L001_R1_001_trimmed.fq.gz \
${trimmed}/6_GCCAAT_L001_R1_001_trimmed.fq.gz \
${trimmed}/7_CAGATC_L001_R1_001_trimmed.fq.gz \
${trimmed}/8_ACTTGA_L001_R1_001_trimmed.fq.gz

# Deduplicate bam files

${bismark_dir}/deduplicate_bismark \
--bam \
--single \
*.bam

# Methylation extraction

${bismark_dir}/bismark_methylation_extractor \
--bedgraph \
--counts \
--scaffolds \
--remove_spaces \
--multicore 28 \
--buffer_size 75% \
*deduplicated.bam

# Bismark processing report

${bismark_dir}/bismark2report

#Bismark summary report

${bismark_dir}/bismark2summary

# Sort files for methylkit and IGV

find *deduplicated.bam | \
xargs basename -s .bam | \
xargs -I{} ${samtools} \
sort --threads 28 {}.bam \
-o {}.sorted.bam

# Index sorted files for IGV
# The "-@ 16" below specifies number of CPU threads to use.

find *.sorted.bam | \
xargs basename -s .sorted.bam | \
xargs -I{} /home/shared/samtools-1.8/samtools \
index -@ 28 {}.sorted.bam


```


output
http://owl.fish.washington.edu/Athaliana/20180913_oly_WGBSseq_bismark/




```



## Downloading de-duplicated bams.


```{bash}

```


```{bash}
pwd
```


```{bash}
curl -O  http://owl.fish.washington.edu/Athaliana/20180913_oly_WGBSseq_bismark/1_ATCACG_L001_R1_001_trimmed_bismark_bt2.deduplicated.bam
curl -O  http://owl.fish.washington.edu/Athaliana/20180913_oly_WGBSseq_bismark/2_CGATGT_L001_R1_001_trimmed_bismark_bt2.deduplicated.bam
curl -O  http://owl.fish.washington.edu/Athaliana/20180913_oly_WGBSseq_bismark/3_TTAGGC_L001_R1_001_trimmed_bismark_bt2.deduplicated.bam
curl -O  http://owl.fish.washington.edu/Athaliana/20180913_oly_WGBSseq_bismark/4_TGACCA_L001_R1_001_trimmed_bismark_bt2.deduplicated.bam
curl -O  http://owl.fish.washington.edu/Athaliana/20180913_oly_WGBSseq_bismark/5_ACAGTG_L001_R1_001_trimmed_bismark_bt2.deduplicated.bam
curl -O  http://owl.fish.washington.edu/Athaliana/20180913_oly_WGBSseq_bismark/6_GCCAAT_L001_R1_001_trimmed_bismark_bt2.deduplicated.bam
curl -O  http://owl.fish.washington.edu/Athaliana/20180913_oly_WGBSseq_bismark/7_CAGATC_L001_R1_001_trimmed_bismark_bt2.deduplicated.bam
curl -O  http://owl.fish.washington.edu/Athaliana/20180913_oly_WGBSseq_bismark/8_ACTTGA_L001_R1_001_trimmed_bismark_bt2.deduplicated.bam
```




curl -O  http://owl.fish.washington.edu/Athaliana/20180913_oly_WGBSseq_bismark/1_ATCACG_L001_R1_001_trimmed_bismark_bt2.deduplicated.bam
curl -O  http://owl.fish.washington.edu/Athaliana/20180913_oly_WGBSseq_bismark/1_ATCACG_L001_R1_001_trimmed_bismark_bt2.deduplicated.bam
curl -O  http://owl.fish.washington.edu/Athaliana/20180913_oly_WGBSseq_bismark/1_ATCACG_L001_R1_001_trimmed_bismark_bt2.deduplicated.bam
curl -O  http://owl.fish.washington.edu/Athaliana/20180913_oly_WGBSseq_bismark/1_ATCACG_L001_R1_001_trimmed_bismark_bt2.deduplicated.bam
curl -O  http://owl.fish.washington.edu/Athaliana/20180913_oly_WGBSseq_bismark/1_ATCACG_L001_R1_001_trimmed_bismark_bt2.deduplicated.bam
curl -O  http://owl.fish.washington.edu/Athaliana/20180913_oly_WGBSseq_bismark/1_ATCACG_L001_R1_001_trimmed_bismark_bt2.deduplicated.bam
curl -O  http://owl.fish.washington.edu/Athaliana/20180913_oly_WGBSseq_bismark/1_ATCACG_L001_R1_001_trimmed_bismark_bt2.deduplicated.bam
curl -O  http://owl.fish.washington.edu/Athaliana/20180913_oly_WGBSseq_bismark/1_ATCACG_L001_R1_001_trimmed_bismark_bt2.deduplicated.bam




```{bash}
find ../data_06/*deduplicated.bam \
| xargs basename -s _L001_R1_001_bismark_bt2.deduplicated.bam | xargs -I{} /home/shared/samtools-1.8/samtools \
sort ../data_06/{}_L001_R1_001_bismark_bt2.deduplicated.bam -o ../data_06/{}_dedup.sorted.bam
```
```{r}
file.list_06=list(  '../data_06/1_ATCACG_dedup.sorted.bam',
                 '../data_06/2_CGATGT_dedup.sorted.bam',
                 '../data_06/3_TTAGGC_dedup.sorted.bam',
                 '../data_06/4_TGACCA_dedup.sorted.bam',
                 '../data_06/5_ACAGTG_dedup.sorted.bam',
                 '../data_06/6_GCCAAT_dedup.sorted.bam',
                 '../data_06/7_CAGATC_dedup.sorted.bam',
                 '../data_06/8_ACTTGA_dedup.sorted.bam'
)
```



```{r}
myobj_06_10x = processBismarkAln(location = file.list_06, sample.id = list("1","2","3","4","5","6","7","8"), assembly = "v081", read.context="CpG", mincov=10, treatment = c(0,0,0,0,1,1,1,1))
```

```{r}
save(myobj_06_10x, file = "../analyses/myobj_06_10x")

```


```{r}
meth_06_10x=unite(myobj_06_10x)
```

```{r}
clusterSamples(meth_06_10x, dist="correlation", method="ward", plot=TRUE)

```


```{r}
myobj_06_3x = processBismarkAln(location = file.list_06, sample.id = list("1","2","3","4","5","6","7","8"), assembly = "v081", read.context="CpG", mincov=3, treatment = c(0,0,0,0,1,1,1,1))
```